Telemetry Module for Solar Vehicle

### 2021-06-14 documentation/FinalPaper/paper.tex
Updates from Overleaf

\subsection{CAN} % Victor
The CAN network in the solar car enables the micro-controllers at each electrical unit in the car to send and receive data without a host computer. This is possible with the special structure of the CAN message.\\
\begin{figure}[h]
    %\centering
    \includegraphics[scale=0.35]{documentation/images/detailed-can-data-frame-architecture.jpg}
    \caption{Structure of a CAN frame}
    \label{fig:CANframe}
\end{figure}\\
The frame uses an identifier to tell which messages goes to which unit. When two messages tries to access the bus, the one with the highest priority, lowest ID, will be granted access to the bus, while the other message has to wait. After the ID comes the RTR bit which determines whether the frame is set to be at sent or received by the node. The control field, sometimes called DLC, tells the amount of bytes used in the following frame field with actual data. The rest of the fields in fig. \ref{fig:CANframe} is not important concerning the nodes ability to communicate across the CAN network.\\
The CAN bus itself is two twisted wires, CAN High and CAN Low. These control the bits in the CAN message by setting a dominant and recessive voltage, which corresponds to a 0 and 1 respectively. A 1 is seen when the voltage in both wires is 2.5V while a 0 is seen when the CAN High wire is driven by 3.5V and the CAN Low wire is driven at 2.5V. 
\subsection{RF module} % Steffan 
The nRF24L01+ LoRa RF module is used to provide two-way communication between the solar car and support vehicle. The module includes a detachable antenna, power amplifier and low-nose amplifier to provide a theoretical range in excess of 1000 m at data rates of up to 2 Mbit/s.  In addition to this, comprehensive driver libraries are provided by the manufacturer, making it very easy to integrate with our project. \\

\subsection{Message protocol}
The nRF24L01+ module uses the Enhanced Shockburst $\copyright$ packet structure to transmit messages over the 2.4 GHz ISM band. Messages contain a data payload of up to 32 bytes, allowing us to transmit one CAN telemetry message per cycle. Further, the package structure includes a preamble, address, packet and CRC byte segments as shown in Figure X. These are all generated automatically when a call to the radio write function is made, and therefore fall outside the scope of this project.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/MessageTypes.pdf}
    \caption{The }
    \label{fig:my_label}
\end{figure}

@@

\subsection{Solar Car} 
\subsubsection{Black Box} % tjark
\subsubsection{CAN transceiver}
\subsection{Support Vehicle}
\subsubsection{GUI} % tjark
\subsubsection{RF transceiver}

>>>>

\subsection{CAN} % Victor
The CAN network in the solar car enables the micro-controllers at each electrical unit in the car to send and receive data without a host computer. This is possible with the special structure of the CAN message.\\
\begin{figure}[h]
    %\centering
    \includegraphics[scale=0.35]{documentation/images/detailed-can-data-frame-architecture.jpg}
    \caption{Structure of a CAN frame}
    \label{fig:CANframe}
\end{figure}\\
The frame uses an identifier to tell which messages goes to which unit. When two messages tries to access the bus, the one with the highest priority, lowest ID, will be granted access to the bus, while the other message has to wait. After the ID comes the RTR bit which determines whether the frame is set to be at sent or received by the node. The control field, sometimes called DLC, tells the amount of bytes used in the following frame field with actual data. The rest of the fields in fig. \ref{fig:CANframe} is not important concerning the nodes ability to communicate across the CAN network.\\
The CAN bus itself is two twisted wires, CAN High and CAN Low. These control the bits in the CAN message by setting a dominant and recessive voltage, which corresponds to a 0 and 1 respectively. A 1 is seen when the voltage in both wires is 2.5V while a 0 is seen when the CAN High wire is driven by 3.5V and the CAN Low wire is driven at 2.5V. 
\subsection{RF module} % Steffan 
The nRF24L01+ LoRa RF module is used to provide two-way communication between the solar car and support vehicle. The module includes a detachable antenna, power amplifier and low-noise amplifier to provide a theoretical range in excess of 1000 m at data rates of up to 2 Mbit/s.  In addition to this, comprehensive driver libraries are provided by the manufacturer, making it very easy to integrate with our project.

\subsection{Message protocol}
The radio connection is the pivot point of the telemetry system and a flexible way to pass commands and associated payloads both ways is needed. 
The nRF24L01+ module uses the Enhanced Shockburst $\copyright$ packet structure to transmit messages over the 2.4 GHz ISM band. Messages contain a data payload of up to 32 bytes, allowing us comfortably to transmit one CAN telemetry message per packet. Further, the package structure includes a preamble, address, packet and CRC bytes segments as shown in Figure \ref{fig:shockburst}. These are all generated automatically when a call to the radio write function is made, and therefore fall outside the scope of this project.   
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.png}
    \caption{The Enhanced Shockburst $\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/MessageTypes.pdf}
    \caption{The }
    \label{fig:my_label}
\end{figure}

@@

\subsection{Solar Car} 
\subsubsection{Black Box} % tjark

The black box functionality in the solar car is implemented using a SD card. The Teensy 3.6 used as a microcontroller in the telemetry module of the solar car already includes a 4-bit

\subsubsection{CAN transceiver}
\subsection{Support Vehicle}
\subsubsection{GUI} % tjark
\subsubsection{RF transceiver}
